Spin canonical divisors of log stacky curves

### 2015-06-20 stacky_write_up/spin_cring.tex
finished genus 0 induction

\section{Introduction}
This is our project.
Example, O'Dorney's paper \cite{dorney:canonical}.
We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. \todo{Rewrite this to be more precise}
\end{thm}
\begin{proof}

@@

\section{Background}
Here are some definitions.
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.

@@

\begin{lem}
\label{lem:minimal_quadratic}

\end{lem}
\begin{proof}

>>>>

\section{Introduction}
\todo{Edit this stuff}
This is our project.
Example, O'Dorney's paper \cite{dorney:canonical}.
We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,L)$ be a tame log spin curve over a perfect field $k$, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$. Then the canonical ring 
\begin{align*}
	R(\sx,L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
\end{align*}
is generated as a $k$-algebra by elements of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions. \todo{Include reference to the table with this list of exceptions.}
\end{thm}
\begin{proof}

@@

\section{Background}
\todo{edit this}
Here are some definitions.
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.

@@

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily generated in degree 1, is equipped with a monomial ordering $\prec.$ Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded rings with kernel $I,$ such that $I$ is generated by elements $f_1,\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$ is of the form $x_k$. Then, the elements $f_i$ determine minimal generators for $I$.
\end{lem}
\begin{proof}
Regrade the ring $k[x_1,\ldots, x_n]$ so that all $x_i$ lie in degree 1. Then, $\phi:k[x_1,\ldots, x_n]\rightarrow B$ determines a map of rings, no longer necessarily graded. Consider the grlex monomial ordering $<$ on $k[x_1,\ldots, x_n]$. By assumption, the kernel $I$ is generated by elements whose initial terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of generators for $I$ must have at least $j$ elements. Since $f_1,\ldots, f_j$ is such a set, it is minimal.
\end{proof}
